Fleet Definitions

### 2021-02-26 docs/GBFleetDefinitions.Rmd
updated index.html

A dendrogram (Figure \@ref(fig:dendro1)) is then formed using the agglomerative hierarchical process. This process is carried out using the statistical package `cluster`(@cluster211) in R.

```{r cluster1, echo=T,eval=F}
clusterObj <- cluster_analysis_all_gears()
plot(clusterObj,ask=T,which.plots=2,main="Complete gear list using 90% landing from each gear",xlab="")
#' 
```
```{r dendro1,out.width="100%",fig.cap="The denrogram obtained from a nearest-neighbor, hierarchical cluster analysi on all gears used in the Georges Bank Ecological Production unit defined by Statistical areas"}
knitr::include_graphics("figures/dendrogram1.png")
```

>>>>

A dendrogram (Figure \@ref(fig:dendro1)) is then formed using the agglomerative hierarchical process. This process is carried out using the statistical package `cluster`(@cluster211) in R. Initial inspection indicates further "cleaning" of the data is required.

```{r cluster1, echo=T,eval=F}
clusterObj <- cluster_analysis_all_gears()
plot(clusterObj,ask=T,which.plots=2,main="Complete gear list using 90% landing from each gear",xlab="")

```
```{r dendro1,out.width="100%",fig.cap="The denrogram obtained from a nearest-neighbor, hierarchical cluster analysi on all gears used in the Georges Bank Ecological Production unit defined by Statistical areas"}
knitr::include_graphics("figures/dendrogram1.png")
```
